---
title: "CSE6242"
author: "Mahaveer Jain"
date: "11/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(glmnet)
library(tidyverse)
library(lubridate)
```

## R Markdown
Read the data and convert the Fips as a factor 

```{r cars}
bData = read.csv('allData.csv', header = TRUE)
bData$Fips =  as.factor(bData$Fips)
bData$datetime = ymd(bData$datetime)
bData.time = subset(bData , select = c(datetime, Fips))
#bData  = subset(bData , select = -datetime)
bData  = subset(bData , select = -HPI)
bData  = subset(bData , select = -total_number_hpa)
#create minimum and max model
hFull = lm(HPI_inf~. -  datetime, data = bData)
hLow = lm(HPI_inf~ 1, data = bData)
```

## Including Plots

Perform forward variable selection model

```{r pressure, echo=FALSE}
step(hLow, scope=list(lower=hLow, 
     upper=hFull), direction="forward")
```

Perform elastic Net and lasso model to see if the variables selection differ
```{r}
set.seed(100)
elasticmodel.cv = cv.glmnet(data.matrix(subset(bData , select = -c(datetime, HPI_inf))), y = bData$HPI_inf, alpha=0.5, nfolds=10, type.measure = "mse",  family="gaussian")

elasticmodel = glmnet(data.matrix(subset(bData , select = -c(datetime, HPI_inf))), y = bData$HPI_inf, alpha=0.5, nlambda=100,  family="gaussian")

index.elastic <- which(coef(elasticmodel, elasticmodel.cv$lambda.min) == 0)

```
```{r}
set.seed(100)
lassomodel.cv = cv.glmnet(data.matrix(subset(bData , select = -c(datetime, HPI_inf))), y = bData$HPI_inf, alpha=1, nfolds=10, type.measure = "mse",  family="gaussian")

## Fit lasso model with 100 values for lambda
lassomodel = glmnet(data.matrix(subset(bData , select = -c(datetime, HPI_inf))), y = bData$HPI_inf, alpha=1, nlambda=100,  family="gaussian")
index.lasso <- which(coef(lassomodel, lassomodel.cv$lambda.min) == 0)
```


Build the model using forward variable selection method.
```{r}
bubbleModel = lm(HPI_inf ~ total_number_hpa_seasonality + Real.Estate_seasonality + Unemployment.Rate + zillow_seasonality  + Realtor_seasonality + CCI + Population  + Apartment_seasonality   +
Real.Estate.Agent_seasonality + Rent_seasonality	+ Fips, data = bData)
summary(bubbleModel)
```
Estimate the predicted value and combine with actual value for each state.

```{r}
y = predict(bubbleModel, bData)

data = subset(bData, select = c(datetime, HPI_inf, Fips))
data['HPI_pre'] = y
```

Plot the data
```{r}
library(scales)
data[data['Fips']==6,] %>% 
  ggplot( aes(x=datetime)) +
   geom_line(aes(y = HPI_pre), color = "darkred") +
   geom_line(aes(y = HPI_inf), color = "steelblue") +
  scale_x_date(breaks="year", labels=date_format("%Y"))
   
# + ylim(0,22000) +
#    annotate(geom="text", x=as.Date("2017-01-01"), y=20089, 
#             label="Bitcoin price reached 20k $\nat the end of 2017") +
#    annotate(geom="point", x=as.Date("2017-12-17"), y=20089, size=10, shape=21, fill="transparent") +
#    geom_hline(yintercept=5000, color="orange", size=.5) +
#    theme_ipsum()
```
Plot the fraction of true HPI and estimated HPI

```{r}
data[data['Fips']==6,] %>% 
  ggplot( aes(x=datetime, color = Fips)) +
   geom_line(aes(y = HPI_inf/HPI_pre)) +
  scale_x_date(breaks="year", labels=date_format("%Y"))
```
> data %>% 
+     ggplot( aes(x=datetime, color = Fips)) +
+     geom_line(aes(y = HPI_pre/HPI_inf)) +
+     scale_x_date(breaks="year", labels=date_format("%Y"))

